# Interactive Content with Widgets

We use R packages like `plotly` and `leaflet` to create interactive content.

## Plotly Graph

```{r}
#| echo: true
#| label: fig-plotly-graph
#| fig-cap: "Scatter plot of bill length vs. bill depth in penguins."


library(plotly)
library(palmerpenguins)
data(penguins, package = "palmerpenguins")

plot_ly(data = penguins, x = ~bill_length_mm, y = ~bill_depth_mm, type = 'scatter', mode = 'markers')
```

@fig-plotly-graph shows a scatter plot of bill length vs. bill depth in penguins. You can hover over the points to see the data values. It is created using the `plotly` package.

## Leaflet Map

```{r}
#| label: fig-leaflet-map
#| fig-cap: "Map showing a sample location. Note: Interactive features do not display in PDF."


library(leaflet)

# Placeholder data; replace with actual geographic data if available
leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = 174.768, lat = -36.852, popup = "Auckland")
```

@fig-leaflet-map shows a sample map with a marker at Auckland, New Zealand. It is created using the `leaflet` package. Note that interactive features do not display in PDF.
